Figures

### 2019-05-22 figures/01_county_extent.Rmd
cleanup legends

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r lagos_setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
# setwd("_episodes_rmd")
library(vapour)
library(LAGOSNE)
library(magrittr)
library(dplyr)
library(lme4)
library(sf)
library(units)
library(merTools)
library(ggplot2)
library(cowplot)
library(ggridges)
library(tidyr)
library(ggExtra)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r lagos_setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
# library(LAGOSNE)
# library(magrittr)
# library(dplyr)
# library(lme4)
# library(sf)
# library(units)
# library(merTools)
# library(ggplot2)
# library(cowplot)
# library(ggridges)
# library(tidyr)
# library(ggExtra)

@@

```{r tptn_maps, echo=FALSE}
ep         <- readRDS("../data/ep.rds")

mround <- function(x, base){
        base * round(x / base)
}

q_breaks <- function(x, var_name){
  # x <- ep
  # var_name <- "tn"
  qs              <- c(mround(quantile(as.numeric(as.data.frame(x[,var_name])[,1]), na.rm = TRUE), 5))
  labels          <- as.character(qs)
  res             <- cut(as.numeric(as.data.frame(x[,var_name])[,1]), 
                         breaks = c(qs, Inf), 
                         labels = as.character(qs), 
                         include.lowest = TRUE)

  levels(res)[1]  <- paste0("> ", levels(res)[1])
  levels(res)[length(levels(res))] <- 
    paste0("> ", levels(res)[length(levels(res))])
  res
}

plot_opts <- theme_void() + 
  theme(title = element_text(size = 10), 
        # legend.position = "bottom", 
        panel.border = element_rect(colour = "black", fill = NA, size=1), 
        legend.spacing.x = unit(0.000001, "cm"), 
        legend.direction = "horizontal", 
        legend.position = "bottom", 
        legend.justification = "left")

ep$plot_breaks <- q_breaks(ep, "tp")

gg_tp <- ggplot() +
  geom_sf(data = state_intersects) +
  geom_sf(data = dplyr::filter(coordinatize(ep), !is.na(tp)), 
          aes(color = plot_breaks), show.legend = "point", size = 0.7) +
  scale_color_viridis_d() +
  labs(color = "tp") +
  coord_sf(datum = NA) +
  plot_opts

ep$plot_breaks <- q_breaks(ep, "tn")

gg_tn <- ggplot() +
  geom_sf(data = state_intersects) +
  geom_sf(data = dplyr::filter(coordinatize(ep), !is.na(tn)), 
          aes(color = plot_breaks), show.legend = "point", size = 0.7) +
  scale_color_viridis_d() +
  labs(color = "tn") +
  coord_sf(datum = NA) +
  guides(color = guide_legend(nrow = 1)) +
  plot_opts

# View(ep[,c("tn", "plot_breaks")])

plot_grid(gg_tp, 
          ggplot() + geom_blank(), gg_tn,
          nrow = 1, rel_widths = c(1, 0.1, 1))
```

### 2019-05-22 manuscript/figures.Rmd
add cdl vs nlcd map
cleanup legends

>>>>

```{r maps, fig.cap = "Quanitle map of lake nutrients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```
